Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
Stressed time benefit in experimental section
Added head-to-head comparison of median time.

For the majority of our benchmarks, the conjecture stands that the abstraction-based back-end
is faster than the basic multi-staged verification approach. However, it does fail to
find solutions to 3 benchmarks, as compared to 2 with the multi-staged back-end, where
the numbers given in the discretization matrices are too small. In direct comparison the
abstraction-based is able to find a solution in approximately 35\% of the time required
using the multi-staged back-end. The two back-ends complement each other well in their
benchmark coverage and together solve all benchmarks provided in the set.

>>>>

For the majority of our benchmarks, the conjecture stands that the abstraction-based back-end
is faster than the basic multi-staged verification approach. However, it does fail to
find solutions to 3 benchmarks, as compared to 2 with the multi-staged back-end, where
the numbers given in the discretization matrices are too small. In direct comparison, the
abstraction-based approach is on average able to find a solution in approximately 35\% of
the time required using the multi-staged back-end, and has a median runtime 1.15\,s, which is
seven times smaller than the multi-staged approach. The two back-ends complement each other
in benchmark coverage and together solve all benchmarks in the set.
